\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-27 paper.tex
worked on various sections

On September 10\textsuperscript{th} Atticus Sims presented us with a storyboard
for the app experience. We would not be able to resume work until September
17\textsuperscript{th} due to prior travel plans. Whether Atticus knew this or
not, the design he put forth had ramifications that rippled throughout the
entire software stack we had constructed up to this point.
Figure~\ref{fig:adobeXdDesign} shows this design.

@@

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI. This was disappointing to us, since we spent
a great deal of effort projecting images into the 3D world using the AR camera;
we felt like we figured out how to use this technology in a way that was both
usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
the 3D world, such as by framing the images in a traditional Japanese pagoda,
which would fit in with the environment. On the same screen, there is a
scrollable window of text for a transcript of the audio. Because of this, the
Editour UI and tour metadata JSON file needed to be updated to accommodate a
transcript per region. On top of this, the C\# code that interprets the tour
file needed to be updated to expect an audio transcript field.
Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
to add these new features. The arrows next to the region name can be used to
move the ``Region Card'' up and down in the side bar. In the ``Media'' tab, there
is also a text area to include a transcript of the uploaded audio file.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption[Additions to the Editour to accommodate the new design]
    {Additions to the Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps~\autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience.
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkaku-ji for us to use as
image targets. Hikaru Inoue helped us by translating all of the text in these
photos from Japanese to English. In this design, the AR camera superimposes an
``info'' button on top of the sign. Tapping on this button brings up a separate
UI element containing the translation, which can be seen in
Figure~\ref{fig:signTranslation}.

@@

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store, called ``Experience Importer - Adobe Xd files importer'', which claims
``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
objects. They're already there! Just drag .xd file to project and...
voila!''~\autocite{glasseye2019}.  We suspect this sounds too good to be true
because it is. As of September 20\textsuperscript{th}, 2019, there are 6 user
reviews. All of the five-star reviews were have the caveat ``Reviewer was gifted
package by publisher'' which which we interpreted as a warning sign. Because of
this, we decided to rebuild the UI largely from the ground up, using the Adobe XD
file to guide us.

@@

Because the Editour is intended only to be a tool to aid Atticus in creating
tours, not an application for the general public, our user testing of it was less
rigid.

>>>>

By the end of the project, we were able to turn ARuko into an app rich with
features and polish. However, many of these features were presented to us
relatively late into the project. This section discusses some of our initial
concerns when we were first given the task of bringing Atticus' experience
design to life.

On September 10\textsuperscript{th} Atticus Sims presented us with a storyboard
for the app experience. We would not be able to resume work until September
17\textsuperscript{th} due to prior travel plans. The design he put forth had
ramifications that rippled throughout the entire software stack we had
constructed up to this point.  Figure~\ref{fig:adobeXdDesign} shows the experience
design document created in Adobe XD.

@@

The inclusion of a ``chapter selection'' screen had other notable design
implications as well. Initially different regions were triggered solely by your
GPS location. Walking into a region would prompt the available images to change
on screen. Also, a new audio track would begin to play. This forced us to
answer certain basic questions about the chapter select screen for ourselves.
For example, consider a user that steps into one region, triggering the audio
and images. Then, that user selects a chapter from the chapter selection menu,
overriding the ``true'' region the user is physically standing inside of. When
does the GPS ``take over'' again? Should the region change back to the ``true''
region once the audio of the selected region finishes? This might be intuitive
and preferred for most users, but what if the user is more interested in the
image gallery than the audio? Then, the persistence of the image gallery is
strangely tied to the duration of the audio track playing underneath. What if a
user selects a chapter, and then physically enters that region moments later?
Should the audio restart to indicate that the user has arrived at the location?
Or, will this appear as though the audio track the user was already listening
to skipped to the beginning again for no reason? As you can imagine, this
seemingly minor inclusion created a significant amount of discussion.

Other concerns about the chapter selection feature were technical. For a long
time, we were working under the assumption that regions would only be triggered
by GPS location. Because of this long-standing assumption, we were uncertain
about what bugs implementing a chapter selection feature would introduce.

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI.

With more time, we might have been able to get the ground-plane image placement
feature to a state where Atticus might have liked it. We wanted to explore ways
to theme the 2D images in the 3D world, such as by framing the images in a
traditional Japanese pagoda. We had already spent two weeks on this feature, so
dropping this feature was a setback we had to plan around.

On the same screen, there is a scrollable window of text for a transcript of
the audio. Because of this, the Editour UI and tour metadata JSON file needed
to be updated to accommodate one transcript per region. On top of this, the C\#
code that interprets the tour file needed to be updated to expect an audio
transcript field.  Figure~\ref{fig:editourAdditions} shows the UI elements that
changed in order to add these new features. The arrows next to the region name
can be used to move the ``Region Card'' up and down in the side bar. In the
``Media'' tab, there is also a text area to include a transcript of the
uploaded audio file.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption{Additions to the Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps~\autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience.
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project. Luckily,
these changes were still manageable to implement.

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkaku-ji for us to use
as image targets. Hikaru Inoue helped us by translating all of the text in
these photos from Japanese to English. In this design, the AR camera
superimposes an ``info'' button on top of the sign. Tapping on this button
brings up a separate UI element containing the translation, which can be seen
in Figure~\ref{fig:signTranslation}. The details of this feature is discussed
more thoroughly in Section~\ref{sec:translationFeature}.

@@

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store called ``Experience Importer - Adobe Xd files importer.'' The download
page for this extension claims ``Transfer AdobeXd project directly to Unity.
Forget about hours of positioning objects. They're already there! Just drag .xd
file to project and...  voila!''~\autocite{glasseye2019}.  We suspect this
sounds too good to be true because it is. As of September
20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
reviews were have the caveat ``Reviewer was gifted package by publisher'' which
which we interpreted as a warning sign. Because of this, we decided to rebuild
the UI largely from the ground up, using the Adobe XD file to guide us.
%TODO refer to the section that discusses building the ui

@@

Because the Editour is intended only to be a tool to aid Atticus in creating
tours our user testing was less rigid. Even so, the frontend and backend we
built for Editour ended up being largely reliable. The main source of
reliability issues stemmed from the hosting provider, which was out of our
control.
